---
title: Processing the MERSCOPE Ovarian Patient 9 Slice 1 dataset
author: Estella Yixing Dong
date: "November 10, 2023"
output:
  BiocStyle::html_document:
    titlecaps: false
    toc_float: true
bibliography: /ref.bib
---


```{r style, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
library(BiocStyle)
knitr::opts_chunk$set(error=FALSE, message=FALSE, warning=FALSE)
```

# Downloading the count data

We obtain a single-cell RNA sequencing dataset of Xenopus tail cells from ...TODO
We download and cache the count matrix and metadata using the `r Biocpkg("BiocFileCache")` package.

We load the counts into memory.

```{r}
# TODO: change to url
cosmx_lung_p9s1_path <- "~/Desktop/SampleData/Raw/Nanostring_CosMx/Lung/P9/S1"
counts <- read.csv(file.path(cosmx_lung_p9s1_path, "cell_by_gene.csv")) # 91992   982
meta <- read.csv(file.path(cosmx_lung_p9s1_path, "cell_metadata.csv"))  # 91972    20
```

# Subset to a small region for demo data

```{r}
library(dplyr)
counts_test <- counts %>%
  dplyr::filter(fov %in% c(10, 11)) %>%
  dplyr::filter(cell_ID != 0)# take 2 fov, around 1/10 of the original # of cells

meta_test <- meta %>%
  right_join(counts_test[, c("fov", "cell_ID")], by = c("fov", "cell_ID")) %>%
  select("fov", "cell_ID", "Area", "CenterX_local_px", "CenterY_local_px", "CenterX_global_px", "CenterY_global_px")
```

# Saving for upload 

We save the annotated Chromium to file for upload to `r Biocpkg("ExperimentHub")`.

```{r}
cosmx_lung_p9s1_demo_path <- "~/Desktop/SampleData/Raw/Nanostring_CosMx/Lung/P9/test_small_demo"
write.csv(counts_test, file.path(cosmx_lung_p9s1_demo_path, "small_lung_p9s1_exprMat_file.csv"), row.names = FALSE)
write.csv(meta_test, file.path(cosmx_lung_p9s1_demo_path, "small_lung_p9s1_metadata_file.csv"), row.names = FALSE)

cos_small <- readMerscopeSXE(cosmx_lung_p9s1_demo_path)
repath <- file.path("scSpatialExperimentData", "CosMx")
saveRDS(cos_small, file.path(repath, "smallCos_p9s1.rds"))
```

# Session information

```{r}
sessionInfo()
```

# References