---
title: Processing the MERSCOPE Ovarian Patient 2 Slice 2 dataset
author: Estella Yixing Dong
date: "November 10, 2023"
output:
  BiocStyle::html_document:
    titlecaps: false
    toc_float: true
bibliography: /ref.bib
---


```{r style, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
library(BiocStyle)
knitr::opts_chunk$set(error=FALSE, message=FALSE, warning=FALSE)
```

# Downloading the count data

We obtain a single-cell RNA sequencing dataset of Xenopus tail cells from ...TODO
We download and cache the count matrix and metadata using the `r Biocpkg("BiocFileCache")` package.

We load the counts into memory.

```{r}
# TODO: change to url
mer_ovarian_p2s2_path <- "~/Desktop/SampleData/Raw/Vizgen_MERSCOPE/Ovarian/P2/S2"
counts <- read.csv(file.path(mer_ovarian_p2s2_path, "OvarianP2S2_cell_by_gene.csv")) # 71381   551
meta <- read.csv(file.path(mer_ovarian_p2s2_path, "OvarianP2S2_cell_metadata.csv"))  # 71381     9
```

# Subset to a small region for demo data

```{r}
library(dplyr)
meta_test <- meta %>%
  dplyr::filter(center_x > 10000 & center_y > 8000) %>%
  select("X", "fov", "volume", "center_x", "center_y")

counts_test <- counts %>%
  mutate(X = cell) %>%
  right_join(meta_test[, c("X", "fov")], by = "X") %>%
  select(-c(X, fov))
```

# Saving for upload 

We save the annotated Chromium to file for upload to `r Biocpkg("ExperimentHub")`.

```{r}
mer_ovarian_p2s2_demo_path <- "~/Desktop/SampleData/Raw/Vizgen_MERSCOPE/Ovarian/P2/p2s2_demo"
write.csv(counts_test, file.path(mer_ovarian_p2s2_demo_path, "small_ovarian_p2s2_cell_by_gene.csv"), row.names = FALSE)
write.csv(meta_test, file.path(mer_ovarian_p2s2_demo_path, "small_ovarian_p2s2_cell_metadata.csv"), row.names = FALSE)

mer_small <- readMerscopeSXE(mer_ovarian_p2s2_demo_path)
repath <- file.path("scSpatialExperimentData", "MERSCOPE")
saveRDS(mer_small, file.path(repath, "smallMer_p2s2.rds"))
```

# Session information

```{r}
sessionInfo()
```

# References